\documentclass{beamer}
\input{preamble}


\title{Computational Morphology}
\author{Lane Schwartz}
\institute[shortinst]{University of Illinois at Urbana-Champaign}

\date{Week 1 of 16}

\begin{document}

% Specify that no bibliography should be printed
\bibliographystyle{plainnat}

\frame{\titlepage}


\section{Logistics}

\frame {
\frametitle{Course web site}

\url{http://computational.linguistics.illinois.edu/lingNNN/SSSYYYY}

\ \\

\ \\

\begin{itemize}
\item Replace NNN with the course number for this course
\item Replace SSS with the current semester (fall or spring)
\item Replace YYYY with the current four-digit year
\end{itemize}

}

\frame{
\frametitle{DRES}

If a student has a disability or condition that requires special consideration, the student is expected to present the requisite letter from the University Division of Disability Resources and Educational Services (DRES) no later than the beginning of the second day of class.

}

\frame{
\frametitle{Github}

\begin{itemize}
\item Github username
\end{itemize}

}


\frame{
\frametitle{Piazza}

\begin{itemize}
\item Course Piazza site linked off course web page
\item Verify that you are enrolled in the course Piazza site
\item Ask questions via Piazza
\item Do not ask questions via email
\end{itemize}

}


\frame{
\frametitle{i$>$clicker}

\begin{itemize}
\item We will use i$>$clicker in this class.
\item You must have a physical i$>$clicker.
\item You must bring your i$>$clicker to every class session.
\item You must always have working batteries.
\item Your i$>$clicker must be registered.
\end{itemize}

}


\section{Expectations}


\frame{
\frametitle{Academic Integrity}

This course follows the University of Illinois Student Code regarding Academic Integrity. The College of Liberal Arts and Sciences also has an excellent web page on the topic. You are expected to read these resources prior to the second day of class, and to understand your responsibilities with regard to Academic Integrity.
%
All work submitted for this class must be solely your own. Violations of Academic Integrity include, but are not limited to, copying, cheating, and unapproved collaboration. 

\ \\

\textbf{Violations will not be tolerated.}

}

\frame{
\frametitle{Expectations}

\begin{itemize}
\item Command line proficiency
\item Basic competence with git and \LaTeX
\item Basic linguistic competence
\item Self-motivation to learn and read
\item Ability to write in academic style
\end{itemize}

}

\section{Course Overview}

\frame{
\frametitle{Computational Morphology}

\begin{itemize}
\item Motivation for computational morphology
\item Computational modelling
\item Morphology and phonology
\item Finite state toolkits
\item Building finite-state models of language
\item Applications for morphological analyzers
\item Alternative approaches
\end{itemize}

}


\frame{
\frametitle{Motivation}

\begin{itemize}
\item Why computational morphology?
\end{itemize}

}





\frame{
\frametitle{Computational Modelling}

  \begin{itemize}
    \item Set theory
    \item Relations and functions
    \item Theory of computation
    \item Chomsky hierarchy
    \item Regular languages
    \item Finite state machines
    \item Regular expressions
  \end{itemize}

}

\frame{
\frametitle{Morphology and phonology}

\begin{itemize}
\item Study of the shapes and sounds of words
\end{itemize}

}


\frame{
\frametitle{Finite state toolkits}

  \begin{itemize}
    \item xfst
    \item foma
  \end{itemize}

} 


\frame{
\frametitle{Building finite-state models of language}

  \begin{itemize}
    \item Planning
    \item Lexicography
    \item Rule building and composition
    \item Testing and debugging
  \end{itemize}

}


\frame{
\frametitle{Alternative approaches}

  \begin{itemize}
    \item Two-level phonology
    \item Supervised learning
    \item Unsupervised learning
  \end{itemize}

}


\frame{
\frametitle{Applications}

  \begin{itemize}
    \item 
    \item 
    \item 
    \item 
    \item 
    \item 
    \item 
    \item 
  \end{itemize}

}





\end{document}
